cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-09 paper-cardinalR.Rmd
Rendered new version

## Generating high-dimensional clustered data

@@

```{r fig-cluster-stats, fig.width=10, fig.height=3, out.width="100%", layout="l-page"}
# Examine the cluster stats
all_stats <- bind_rows(hc_stats, kmeans_stats)
all_stats |>
  pivot_longer(within.cluster.ss:sindex, names_to = "stat", values_to = "value") |>
  ggplot(aes(x=cl, y=value, colour=method)) +
    geom_line() +
    facet_wrap(~stat, ncol=3, scales="free_y") +
    xlab("Number of clusters") +
    ylab("")
```

>>>>

@@

```{r fig-cluster-stats, fig.width=10, fig.height=3, out.width="100%", layout="l-body"}
# Examine the cluster stats
all_stats <- bind_rows(hc_stats, kmeans_stats)
all_stats |>
  pivot_longer(within.cluster.ss:sindex, names_to = "stat", values_to = "value") |>
  ggplot(aes(x=cl, y=value, colour=method)) +
    geom_line() +
    facet_wrap(~stat, ncol=3, scales="free_y") +
    xlab("Number of clusters") +
    ylab("")
```
